---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# specialsource

<!-- badges: start -->
<!-- badges: end -->

{specialsource} is an extension for roxygen2 which provides a single tag
`@code`. When used, this tag will insert a copy of the function's source code
under the subheading *Source Code*:

```{r}
library(specialsource)

text <- "
#' My function
#' 
#' Add two numbers together
#' 
#' @md
#' 
#' @param x,y Numbers to add
#' 
#' @code The source is included for those who want to know the details
#' 
#' @examples
#' f(1, 2)
f <- function(x, y) {
  # Add x and y
  x + y
}
"

roxygen2::roc_proc_text(roxygen2::rd_roclet(), text)
```

# Why?

Good code should be, at some level, self-documenting. In certain contexts, source
code is informative enough that it would be nice to see it, complete with
comments, when viewing function documentation with `?` or `help()`, or on a 
website built with pkgdown. The `@code` tag from specialsource exists to provide 
this functionality.

# Installation

This package can be installed from GitHub as follows:
```{r eval=FALSE}
remotes::install_github("wurli/specialsource")
```

